---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FMDSeroMonitor

<!-- badges: start -->
<!-- badges: end -->

The goal of FMDSeroMonitor is to estimate the state and national level sero conversion parameters against FMD vaccination, access the impact of a vaccination and estimation of herd immunity against FMD

## Installation

You can install the development version of FMDSeroMonitor like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(FMDSeroMonitor)
## basic example code
```

SeroMonitor(Prevac = prevac, Postvac = postvac, Census_Data = census)
head(prevac)
                  Sample.size Protected.sample
Andaman & Nicobar         364               61
Andhra Pradesh           4841              727
Arunachal Pradesh         186                5
Assam                    1989              185
Chandigarh                200               71
Chhattisgarh             2152               17

head(postvac)
                  Sample.size Protected.sample
Andaman & Nicobar         516              203
Andhra Pradesh           4832             1745
Assam                    1401              224
Chandigarh                200              151
Chhattisgarh             2011              766
Delhi                     247              241

head(census)
                  Population
Andhra Pradesh       4600087
Arunachal Pradesh     339221
Assam               10909239
Bihar               15397980
Chandigarh             13440
Chhattisgarh         9983954

results will come as

$StateEst.Prevaccination
                  Protectd(%) Variance SE(%) ME(%) CV(%)
Andaman & Nicobar       16.76 3.80e-04  1.95  3.82 11.64
Andhra Pradesh          15.02 2.63e-05  0.51  1.01  3.42
Arunachal Pradesh        2.69 1.41e-04  1.19  2.33 44.22
Assam                    9.30 4.24e-05  0.65  1.28  7.00
Chandigarh              35.50 1.13e-03  3.37  6.60  9.48


